Simulations of fold number selection in cross-validation of linear and LASSO regression

### 2023-06-02 manuscript/manuscript.Rmd
“June2”

We perform an additional 1000 simulations predicting $Y$ as $\hat{Y}$ by LASSO regression instead of linear regression for each $k \in$ {2, 10, $n$/10, 2$n$/10, 3$n$/10, ..., $n$} for each $n \in$ {250, 500, 750, 1000}. To avoid data leakage, we introduce an inner 5-fold cross-validation loop for the selection of parameter $\lambda$ as in the minimization of
$$\sum_{i=j}^{p}(Y_j - \beta_j)^2 + \lambda\sum_{j=1}^{p}|\beta_j|.$$

@@

To estimate $k_\mathrm{optimal}*$ for each $n$, we first fit to the dataset $(k,A)$ for each sample size $n$ a non-linear least squares model of the form
$$\hat{A}(k) = Bk + C + Dk^{-1} + Ek^{-2}$$
with constants $B$ to $E$ specific to each $n$ and constants $B$ and $E$ set to zero for linear regression. We then draw a line $L$ through $(k_1, \hat{A}_1)$ and $(k_n, \hat{A}_n)$ and maximize the perpendicular distance $d$ of each point on $\hat{A}$ from $L$, so that $k_\mathrm{optimal}^* = {\arg\max}_k{d[\hat{A}(k)-L]}$.

>>>>

We perform an additional 1000 simulations predicting $Y$ as $\hat{Y}$ by LASSO regression instead of linear regression for each $k \in$ {2, 10, 20, 30, ..., 100, $n$} for each $n \in$ {250, 500, 750, 1000}. To avoid data leakage, we introduce an inner 5-fold cross-validation loop for the selection of parameter $\lambda$ as in the minimization of
$$\sum_{i=j}^{p}(Y_j - \beta_j)^2 + \lambda\sum_{j=1}^{p}|\beta_j|.$$

@@

To estimate $k_\mathrm{optimal}*$ for each $n$, we first fit to the dataset $(k,A)$ for each sample size $n$ a non-linear least squares model of the form
$$\hat{A}(k) = Bk + C + Dk^{-1} + Ek^{-2}$$
with constants $B$ to $E$ specific to each $n$ and constants $B$ and $E$ set to zero for linear regression. We then draw a line $L$ through $(k_1, \hat{A}_1)$ and $(k_n, \hat{A}_n)$ and maximize the perpendicular distance $d$ of each point on $\hat{A}$ from $L$, so that
$$k_\mathrm{optimal}^* = {\arg\max}_k{d[\hat{A}(k)-L]}.$$

### 2023-06-02 manuscript/manuscript.tex
“June2”

We perform an additional 1000 simulations predicting \(Y\) as
\(\hat{Y}\) by LASSO regression instead of linear regression for each
\(k \in\) \{2, 10, \(n\)/10, 2\(n\)/10, 3\(n\)/10, \ldots, \(n\)\} for
each \(n \in\) \{250, 500, 750, 1000\}. To avoid data leakage, we
introduce an inner 5-fold cross-validation loop for the selection of
parameter \(\lambda\) as in the minimization of
\[\sum_{i=j}^{p}(Y_j - \beta_j)^2 + \lambda\sum_{j=1}^{p}|\beta_j|.\]

@@

To estimate \(k_\mathrm{optimal}*\) for each \(n\), we first fit to the
dataset \((k,A)\) for each sample size \(n\) a non-linear least squares
model of the form \[\hat{A}(k) = Bk + C + Dk^{-1} + Ek^{-2}\] with
constants \(B\) to \(E\) specific to each \(n\) and constants \(B\) and
\(E\) set to zero for linear regression. We then draw a line \(L\)
through \((k_1, \hat{A}_1)\) and \((k_n, \hat{A}_n)\) and maximize the
perpendicular distance \(d\) of each point on \(\hat{A}\) from \(L\), so
that \(k_\mathrm{optimal}^* = {\arg\max}_k{d[\hat{A}(k)-L]}\).

>>>>

We perform an additional 1000 simulations predicting \(Y\) as
\(\hat{Y}\) by LASSO regression instead of linear regression for each
\(k \in\) \{2, 10, 20, 30, \ldots, 100, \(n\)\} for each \(n \in\)
\{250, 500, 750, 1000\}. To avoid data leakage, we introduce an inner
5-fold cross-validation loop for the selection of parameter \(\lambda\)
as in the minimization of
\[\sum_{i=j}^{p}(Y_j - \beta_j)^2 + \lambda\sum_{j=1}^{p}|\beta_j|.\]

@@

To estimate \(k_\mathrm{optimal}*\) for each \(n\), we first fit to the
dataset \((k,A)\) for each sample size \(n\) a non-linear least squares
model of the form \[\hat{A}(k) = Bk + C + Dk^{-1} + Ek^{-2}\] with
constants \(B\) to \(E\) specific to each \(n\) and constants \(B\) and
\(E\) set to zero for linear regression. We then draw a line \(L\)
through \((k_1, \hat{A}_1)\) and \((k_n, \hat{A}_n)\) and maximize the
perpendicular distance \(d\) of each point on \(\hat{A}\) from \(L\), so
that \[k_\mathrm{optimal}^* = {\arg\max}_k{d[\hat{A}(k)-L]}.\]
